Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-09-13 main_new.tex
updates

We consider a lateral domain, near the sea surface, with locations
$\bx \in \mathcal{M} \subset \mathbf{R^2}$. The two variables of
interest, temperature and salinity, are defined as random processes;
$\xi_a(\bx)$ denotes the temperature (in $^o C$) and $\xi_b(\bx)$
denotes the salinity (in $mg/l$) at location $\bx$. \kc{might be
  clearer if you used 't' for temp and 's' for salinity. 'a' and 'b'
  are somewhat opaque especially further in the text}.  We let $t_a$ be a
threshold for temperature and $t_b$ a threshold for salinity, the
bivariate ES is then defined by:

@@

% The conditional mean $\bm$ will be important in the following
% derivation in Section \ref{sec:sur}.
The calculation of the design criterion in Eq. (\ref{sur}) requires the marginal distribution of the data which is defined via marginalization over $\bxi$ to be
$\by \sim N( \bA \bmu,\bA \bSigma \bA^t+\bR)$. 
However, it turns out that a simplified form of the calculation is possible because the 
conditional mean in Eq (\ref{gp_hat}) is a linear (affine) function of the data $\by$ and the covariance is not a function of the data.
Before knowing the data, the distribution of the conditional mean is
\begin{equation}\label{distxi} \bm \sim N(\bmu , \bPsi), \hspace{3mm}
  \bPsi=\bSigma \bA^t (\bA \bSigma \bA^t+\bR)^{-1} \bA \bSigma.
\end{equation} 
When considering only grid location $\bx$, we can
extract elements from its mean vector and covariance matrix to get the
bivariate distribution \begin{equation}\label{dist_mxi} 
  \bm(\bx) \sim N \left( \begin{bmatrix}
      \mu_{a}(\bx) \\
      \mu_{b}(\bx) \end{bmatrix}, \begin{bmatrix}
      \psi^2_{a}(\bx) & \psi_{a,b}(\bx)\\
      \psi_{a,b}(\bx) & \psi^2_{b}(\bx) \end{bmatrix} \right),
\end{equation}
which is important for the derivation of the closed form solution of the design criteria.

\section{Uncertainty reduction on excursion sets}
\label{sec:sur}

@@

Based on the Gaussian modeling assumptions, the EPs can be computed at any location $\bx$. Without
additional data, Eq.
(\ref{eq:prob}), we have
\begin{eqnarray}\label{eq:prob_mv0}
 p(\bx) &=& P(\xi_a(\bx) \leq t_a, \xi_b(\bx) \leq t_b) \nonumber \\
 &=& \Phi_2 \begin{pmatrix} 
\begin{bmatrix} t_a\\
t_b
\end{bmatrix};
\begin{bmatrix} \mu_{a}(\bx)\\
\mu_{b}(\bx)
\end{bmatrix},\begin{bmatrix}
\sigma_{a}^2(\bx) & \sigma_{a}(\bx)\sigma_{b}(\bx) \gamma(\bx)  \\
\sigma_{a}(\bx)\sigma_{b}(\bx) \gamma(\bx)  & \sigma_{b}^2(\bx)  
\end{bmatrix}\end{pmatrix},
\end{eqnarray}
where $\Phi_2$ is the bivariate Gaussian cumulative distribution
function, and the mean and covariance entries are as defined in Eq. (\ref{gp_bar}).

When data $\by$ are available, Eq. (\ref{eq:post_ep}), we similarly get
\begin{eqnarray}\label{eq:prob_mv}
 p(\bx;\by) &=& P(\xi_a(\bx) \leq t_a, \xi_b(\bx) \leq t_b |\by)
 \nonumber \\
 &=& \Phi_2 \begin{pmatrix} 
\begin{bmatrix} t_a\\
t_b
\end{bmatrix};
\begin{bmatrix} m_{a}(\bx)\\
m_{b}(\bx)
\end{bmatrix},\begin{bmatrix}
s_{a}^2(\bx) & s_{a,b}(\bx)  \\
s_{a,b}(\bx)  & s_{b}^2(\bx)  
\end{bmatrix}\end{pmatrix},
\end{eqnarray}
with parameters as defined in Eq. (\ref{gp_upd}) and (\ref{gp_hat}).

@@

A critical first
element in the derivation is the GP model, and the linear dependence on data $\by$ in the conditional mean in Eq. (\ref{gp_upd}), which means that we have a closed form Gaussian distribution for the conditional mean in Eq. (\ref{dist_mxi}). The high-dimensional inner integral in Eq. (\ref{sur}) then reduces to a bivariate integral \citep{bhattacharjya2013value, chevalier2014fast}, with expectation over $\bm=(m_{a},m_{b})^t$. 
We standardize the two variables in Eq. (\ref{sur}), i.e.
$Z_a=\frac{\xi_a-m_{a}}{s_{a}}$,
$Z_b=\frac{\xi_b-m_{b}}{s_{b}}$, and then
\begin{eqnarray}\label{ytom}
   P(\xi_a \leq t_a, \xi_b \leq t_b|\by) &=& P \left( Z_a \leq\frac{t_a-m_{a}}{s_{a}}, Z_b \leq\frac{t_b-m_{b}}{s_{b}}|\by \right) \nonumber \\
   &=& \Phi_2 \begin{pmatrix} 
\begin{bmatrix} \frac{t_a-m_{a}}{s_{a}}\\
\frac{t_b-m_{b}}{s_{b}}
\end{bmatrix};
 \begin{bmatrix} 0\\
0
\end{bmatrix},\begin{bmatrix}
1 & \eta_{s,t}  \\
\eta_{s,t}   & 1  
\end{bmatrix}\end{pmatrix} \nonumber \\
&=& P(\xi_a \leq t_a, \xi_b \leq t_b|\bm),
\end{eqnarray}
where $\eta_{a,b} =s_{a,b}/(s_{a} s_{b})$.
%Since the expression only depends on $\by$ via $\bm$, the expectation in Eq. (\ref{sur}) is reduced to a bivariate integral over $\bm$ (which will vary for each integrand term, because the locations differ).

Using Eq. (\ref{ytom}) and
introducing $\pi(\bm)$ for the density function of $\bm$, the expected Bernoulli variance becomes
\begin{eqnarray}\label{eq:var2}
E_{\by}(p(1-p)) &=& E_{\bm}(p(1-p)), \hspace{3mm} p=P(\xi_a \leq t_a, \xi_b \leq t_b|\bm) \nonumber \\
E_{\bm}(p(1-p)) & = & \int p[1-p] \pi(\bm) d\bm, \nonumber \\
 &=& \int P(\xi_a \leq t_a, \xi_b \leq t_b|\bm)  \pi(\bm) d\bm \nonumber  \\
&-& \int P(\xi_a \leq t_a, \xi_b \leq t_b|\bm) P(\xi_a \leq t_a, \xi_b \leq t_b|\bm) \pi(\bm) d\bm. 
\end{eqnarray}
We will next extend results of \cite{chevalier2014fast} to solve for these two parts (see also \cite{stroh} who mentioned the possibilities of such extensions).

Considering part I of the, we have
\begin{equation}\label{part1:phi2}
 \int P(\xi_a \leq t_a, \xi_b \leq t_b|\bm) \pi(\bm) d\bm= 
P \left( Z_{a} \leq \frac{t_a-m_{a}}{s_{a}}, 
Z_{b} \leq \frac{t_b-m_{b}}{s_{b}} \right), \nonumber
\end{equation}
where $\bZ=(Z_{a},Z_{b})$ is a bivariate zero-mean and unit-variance Gaussian vector, with $\mbox{Corr}(Z_{a},Z_{b})=\eta_{a,b}$. Moreover, $\bZ$ is chosen to be independent of $\bm$. Using Eq. (\ref{dist_mxi}) we have
\begin{equation}
    E(s_{a} Z_{a}+m_{a}-t_a) = \mu_{a}-t_a, \hspace{3mm}
    \mbox{Var}(s_{a} Z_{a}+m_{a}-t_a) = s^2_a+ \psi^2_{a}, 
\end{equation}
and the same holds for the salinity part with subscript $b$. From this calculation, we get
\begin{eqnarray}\label{two_parts0}
& P & \left( Z_{a} \leq \frac{t_a-m_{a}}{s_{a}}, 
Z_{b} \leq \frac{t_b-m_{b}}{s_{b}} \right) \\
&=& \Phi_2 \begin{pmatrix} 
\begin{bmatrix} 0\\
0
\end{bmatrix};
\begin{bmatrix} \mu_{a}-t_a\\
\mu_{b}-t_b
\end{bmatrix},\begin{bmatrix}
s^2_a+ \psi^2_{a} & s_{a,b}+\psi_{a,b}  \\
s_{a,b}+\psi_{a,b}   & s^2_a+ \psi^2_{a} 
\end{bmatrix}\end{pmatrix} \nonumber.
\end{eqnarray}

For part II of expression (\ref{eq:var2}), standardization means that
\begin{eqnarray}\label{part1:phi4}
&& \int P(\xi_a \leq t_a, \xi_b \leq t_b|\bm) P(\xi_a \leq t_a, \xi_b \leq t_b|\bm) p(\bm) d\bm =  \\
&& P\left( Z_{1,a} \leq \frac{t_a-m_{a}}{s_{a}}, 
Z_{1,b} \leq \frac{t_b-m_{b}}{s_{b}},Z_{2,b} \leq \frac{t_a-m_{a}}{s_{a}}, 
Z_{2,b} \leq \frac{t_b-m_{b}}{s_{b}} \right). \nonumber
\end{eqnarray}
Here,
$\bZ_1=(Z_{1,a},Z_{1,b})$, $\bZ_2=(Z_{2,a},Z_{2,b})$ are independent bivariate zero-mean and unit-variance Gaussian vectors, both with element-wise correlation
$\eta_{a,b}$. Moreover, $\bZ_1$ and $\bZ_2$ are chosen to be independent of $\bm$. Hence,
\begin{equation}
    \left(
    \begin{array}{cccccc}
         Z_{1,a} \\
         Z_{1,b} \\
         Z_{2,a} \\
         Z_{2,b} \\
         m_{a} \\
         m_{b}
    \end{array}
    \right)
\sim N \left(
\left(
    \begin{array}{cccccc}
    0 \\
    0 \\
    0 \\
    0 \\
          \mu_{a} \\
         \mu_{b} 
    \end{array}
    \right),
   \left[ 
      \begin{array}{cccccc}
        1 & \eta_{a,b} & 0 & 0 & 0 & 0  \\
        \eta_{a,b} & 1 & 0 & 0 & 0 & 0 \\
        0 & 0 & 1 & \eta_{a,b} & 0 & 0 \\
        0 & 0 & \eta_{a,b} & 1 & 0 & 0 \\
        0 & 0 & 0 & 0 & \psi^2_{a} & \psi_{a,b} \\
        0 & 0 & 0 & 0 & \psi_{a,b} & \psi^2_{b} 
    \end{array}
\right]
\right).
\vspace{0.2cm}
\end{equation}

The solution to part II is then to evaluate a four-variable cumulative distribution function associated with Eqn. (\ref{part1:phi4}), accounting for the mean, variance and covariances of $\bZ_1$, $\bZ_2$ and $\bm$ in the appropriate linear combinations. Using vector-matrix formulations, we define linear combinations
\begin{equation}\label{Vcomb}
    \bV=\left[
    \begin{array}{cccccc}
        s_a & 0 & 0 & 0 & 1 & 0 \\
         0 & s_b & 0 & 0 & 0 & 1 \\
         0 & 0 & s_a & 0 & 1 & 0\\
         0 & 0 & 0 & s_b & 0 & 1\\
    \end{array}
    \right] 
    \left(
    \begin{array}{cccccc}
         Z_{1,a} \\
         Z_{1,b} \\
         Z_{2,a} \\
         Z_{2,b} \\
         m_{a} \\
         m_{b}
    \end{array}
    \right),
\end{equation}
and the part II calculation becomes
\begin{eqnarray}\label{part1:phi4}
&& P \left( Z_{1,a} \leq \frac{t_a-m_{a}}{s_{a}}, 
Z_{1,b} \leq \frac{t_b-m_{b}}{s_{b}},Z_{2,b} \leq \frac{t_a-m_{a}}{s_{a}}, 
Z_{2,b} \leq \frac{t_b-m_{b}}{s_{b}} \right)  \\
&=&  \Phi_4 
\begin{pmatrix} 
\begin{bmatrix} t_a\\
t_b \\
t_a \\
t_b
\end{bmatrix};
E( \bV),Var(\bV)
\end{pmatrix} \nonumber.
\end{eqnarray}

The multivariate cumulative probabilities in two and four dimensions are fast to compute using methods of \cite{genz2009computation}.
In the end, the part I solution in Eq. (\ref{two_parts0}) and part II solution in Eq. (\ref{part1:phi4}) are computed for each location on the grid, and summing over the $x \in \mathcal{M}_g$, gives the design evaluation criterion in Eq. (\ref{sur}).

>>>>

We consider a lateral domain, near the sea surface, with locations
$\bx \in \mathcal{M} \subset \mathbf{R^2}$. The two variables of
interest, temperature and salinity, are defined as random processes;
$\xi_a(\bx)$ denotes the temperature (in $^o C$) and $\xi_b(\bx)$
denotes the salinity (in $mg/l$) at location $\bx$. \kc{might be
  clearer if you used 't' for temp and 's' for salinity. 'a' and 'b'
  are somewhat opaque especially further in the text. Also there
  should be a statement about why we're considering only 2 variables
  and the impact to considering (algebraically) more in the following
  formulations. This will surely be asked by any reviewer.}.  We let $t_a$ be a
threshold for temperature and $t_b$ a threshold for salinity, the
bivariate ES is then defined by:

@@

% The conditional mean $\bm$ will be important in the following
% derivation in Section \ref{sec:sur}.
The calculation of the design criterion in Eq. (\ref{sur}) requires
the marginal distribution of the data which is defined over $\bxi$ to
be $\by \sim N( \bA \bmu,\bA \bSigma \bA^t+\bR)$.  However, it turns
out that a simplified form of the calculation is possible because the
conditional mean in Eq (\ref{gp_hat}) is a linear (affine) function of
the data $\by$ and the covariance is not a function of the data.
Before knowing the data, the distribution of the conditional mean is
\begin{equation}\label{distxi} \bm \sim N(\bmu , \bPsi), \hspace{3mm}
  \bPsi=\bSigma \bA^t (\bA \bSigma \bA^t+\bR)^{-1} \bA \bSigma.
\end{equation} 
When considering only grid location $\bx$, we can
extract elements from its mean vector and covariance matrix to get the
bivariate distribution \begin{equation}\label{dist_mxi} 
  \bm(\bx) \sim N \left( \begin{bmatrix}
      \mu_{a}(\bx) \\
      \mu_{b}(\bx) \end{bmatrix}, \begin{bmatrix}
      \psi^2_{a}(\bx) & \psi_{a,b}(\bx)\\
      \psi_{a,b}(\bx) & \psi^2_{b}(\bx) \end{bmatrix} \right),
\end{equation}
which is important for the derivation of the closed form solution of the design criteria.

\section{Uncertainty reduction in excursion sets}
\label{sec:sur}

@@

Based on Gaussian modeling assumptions, the EPs can be computed at any
location $\bx$. Without additional data, Eq.  (\ref{eq:prob}) gives us:

\begin{eqnarray}\label{eq:prob_mv0}
 p(\bx) &=& P(\xi_a(\bx) \leq t_a, \xi_b(\bx) \leq t_b) \nonumber \\
 &=& \Phi_2 \begin{pmatrix} 
\begin{bmatrix} t_a\\
t_b
\end{bmatrix};
\begin{bmatrix} \mu_{a}(\bx)\\
\mu_{b}(\bx)
\end{bmatrix},\begin{bmatrix}
\sigma_{a}^2(\bx) & \sigma_{a}(\bx)\sigma_{b}(\bx) \gamma(\bx)  \\
\sigma_{a}(\bx)\sigma_{b}(\bx) \gamma(\bx)  & \sigma_{b}^2(\bx)  
\end{bmatrix}\end{pmatrix},
\end{eqnarray}
where $\Phi_2$ is the bivariate Gaussian cumulative distribution
function, and the mean and covariance entries are as defined in Eq. (\ref{gp_bar}).

When data $\by$ are available, Eq. (\ref{eq:post_ep}) similarly gives
us:
\begin{eqnarray}\label{eq:prob_mv}
 p(\bx;\by) &=& P(\xi_a(\bx) \leq t_a, \xi_b(\bx) \leq t_b |\by)
 \nonumber \\
 &=& \Phi_2 \begin{pmatrix} 
\begin{bmatrix} t_a\\
t_b
\end{bmatrix};
\begin{bmatrix} m_{a}(\bx)\\
m_{b}(\bx)
\end{bmatrix},\begin{bmatrix}
s_{a}^2(\bx) & s_{a,b}(\bx)  \\
s_{a,b}(\bx)  & s_{b}^2(\bx)  
\end{bmatrix}\end{pmatrix},
\end{eqnarray}
with parameters as defined in Eq. (\ref{gp_upd}) and (\ref{gp_hat}).

@@

A critical first element in the derivation is the GP model, and the
linear dependence on $\by$ in the conditional mean in
Eq. (\ref{gp_upd}), which results in a closed form Gaussian
distribution for the conditional mean in Eq. (\ref{dist_mxi}). The
high-dimensional inner integral in Eq. (\ref{sur}) then reduces to a
bivariate integral \citep{bhattacharjya2013value, chevalier2014fast},
with expectation over $\bm=(m_{a},m_{b})^t$.  We standardize the two
variables in Eq. (\ref{sur}), i.e.  $Z_a=\frac{\xi_a-m_{a}}{s_{a}}$,
$Z_b=\frac{\xi_b-m_{b}}{s_{b}}$, and then
\begin{eqnarray}\label{ytom}
   P(\xi_a \leq t_a, \xi_b \leq t_b|\by) &=& P \left( Z_a \leq\frac{t_a-m_{a}}{s_{a}}, Z_b \leq\frac{t_b-m_{b}}{s_{b}}|\by \right) \nonumber \\
   &=& \Phi_2 \begin{pmatrix} 
\begin{bmatrix} \frac{t_a-m_{a}}{s_{a}}\\
\frac{t_b-m_{b}}{s_{b}}
\end{bmatrix};
 \begin{bmatrix} 0\\
0
\end{bmatrix},\begin{bmatrix}
1 & \eta_{s,t}  \\
\eta_{s,t}   & 1  
\end{bmatrix}\end{pmatrix} \nonumber \\
&=& P(\xi_a \leq t_a, \xi_b \leq t_b|\bm),
\end{eqnarray}
where $\eta_{a,b} =s_{a,b}/(s_{a} s_{b})$.
%Since the expression only depends on $\by$ via $\bm$, the expectation in Eq. (\ref{sur}) is reduced to a bivariate integral over $\bm$ (which will vary for each integrand term, because the locations differ).

Using Eq. (\ref{ytom}) and introducing $\pi(\bm)$ for the density
function of $\bm$, the expected Bernoulli variance becomes:
\begin{eqnarray}\label{eq:var2}
E_{\by}(p(1-p)) &=& E_{\bm}(p(1-p)), \hspace{3mm} p=P(\xi_a \leq t_a, \xi_b \leq t_b|\bm) \nonumber \\
E_{\bm}(p(1-p)) & = & \int p[1-p] \pi(\bm) d\bm, \nonumber \\
 &=& \int P(\xi_a \leq t_a, \xi_b \leq t_b|\bm)  \pi(\bm) d\bm \nonumber  \\
&-& \int P(\xi_a \leq t_a, \xi_b \leq t_b|\bm) P(\xi_a \leq t_a, \xi_b \leq t_b|\bm) \pi(\bm) d\bm. 
\end{eqnarray}
We will next extend results of \cite{chevalier2014fast} to solve for
these two parts (see also \cite{stroh} for such an extensions).

For the first part of the above, we have:
\begin{equation}\label{part1:phi2}
 \int P(\xi_a \leq t_a, \xi_b \leq t_b|\bm) \pi(\bm) d\bm= 
P \left( Z_{a} \leq \frac{t_a-m_{a}}{s_{a}}, 
Z_{b} \leq \frac{t_b-m_{b}}{s_{b}} \right), \nonumber
\end{equation}
where $\bZ=(Z_{a},Z_{b})$ is a bivariate zero-mean and unit-variance
Gaussian vector, with $\mbox{Corr}(Z_{a},Z_{b})=\eta_{a,b}$. Moreover,
$\bZ$ is chosen to be independent of $\bm$. Using Eq. (\ref{dist_mxi})
we have
\begin{equation}
    E(s_{a} Z_{a}+m_{a}-t_a) = \mu_{a}-t_a, \hspace{3mm}
    \mbox{Var}(s_{a} Z_{a}+m_{a}-t_a) = s^2_a+ \psi^2_{a}, 
\end{equation}
and the same holds for the salinity part with subscript $b$ \kc{I
  really think this 'a' 'b' business should go and be more descriptive
  or intuitive.}. From this we get:
\begin{eqnarray}\label{two_parts0}
& P & \left( Z_{a} \leq \frac{t_a-m_{a}}{s_{a}}, 
Z_{b} \leq \frac{t_b-m_{b}}{s_{b}} \right) \\
&=& \Phi_2 \begin{pmatrix} 
\begin{bmatrix} 0\\
0
\end{bmatrix};
\begin{bmatrix} \mu_{a}-t_a\\
\mu_{b}-t_b
\end{bmatrix},\begin{bmatrix}
s^2_a+ \psi^2_{a} & s_{a,b}+\psi_{a,b}  \\
s_{a,b}+\psi_{a,b}   & s^2_a+ \psi^2_{a} 
\end{bmatrix}\end{pmatrix} \nonumber.
\end{eqnarray}

For the second part of the expression (\ref{eq:var2}), standardization
implies that: 
\begin{eqnarray}\label{part1:phi4}
&& \int P(\xi_a \leq t_a, \xi_b \leq t_b|\bm) P(\xi_a \leq t_a, \xi_b \leq t_b|\bm) p(\bm) d\bm =  \\
&& P\left( Z_{1,a} \leq \frac{t_a-m_{a}}{s_{a}}, 
Z_{1,b} \leq \frac{t_b-m_{b}}{s_{b}},Z_{2,b} \leq \frac{t_a-m_{a}}{s_{a}}, 
Z_{2,b} \leq \frac{t_b-m_{b}}{s_{b}} \right). \nonumber
\end{eqnarray}
Here, $\bZ_1=(Z_{1,a},Z_{1,b})$, $\bZ_2=(Z_{2,a},Z_{2,b})$ are
independent bivariate zero-mean and unit-variance Gaussian vectors,
both with element-wise correlation $\eta_{a,b}$. Moreover, $\bZ_1$ and
$\bZ_2$ are chosen to be independent of $\bm$. Hence:
\begin{equation}
    \left(
    \begin{array}{cccccc}
         Z_{1,a} \\
         Z_{1,b} \\
         Z_{2,a} \\
         Z_{2,b} \\
         m_{a} \\
         m_{b}
    \end{array}
    \right)
\sim N \left(
\left(
    \begin{array}{cccccc}
    0 \\
    0 \\
    0 \\
    0 \\
          \mu_{a} \\
         \mu_{b} 
    \end{array}
    \right),
   \left[ 
      \begin{array}{cccccc}
        1 & \eta_{a,b} & 0 & 0 & 0 & 0  \\
        \eta_{a,b} & 1 & 0 & 0 & 0 & 0 \\
        0 & 0 & 1 & \eta_{a,b} & 0 & 0 \\
        0 & 0 & \eta_{a,b} & 1 & 0 & 0 \\
        0 & 0 & 0 & 0 & \psi^2_{a} & \psi_{a,b} \\
        0 & 0 & 0 & 0 & \psi_{a,b} & \psi^2_{b} 
    \end{array}
\right]
\right).
\vspace{0.2cm}
\end{equation}

The solution to the second part of the equation above, is then to
evaluate a four-variable cumulative distribution function associated
with Eqn. (\ref{part1:phi4}), accounting for the mean, variance and
covariances of $\bZ_1$, $\bZ_2$ and $\bm$ in the appropriate linear
combinations. Using vector-matrix formulations, we define linear
combinations:
\begin{equation}\label{Vcomb}
    \bV=\left[
    \begin{array}{cccccc}
        s_a & 0 & 0 & 0 & 1 & 0 \\
         0 & s_b & 0 & 0 & 0 & 1 \\
         0 & 0 & s_a & 0 & 1 & 0\\
         0 & 0 & 0 & s_b & 0 & 1\\
    \end{array}
    \right] 
    \left(
    \begin{array}{cccccc}
         Z_{1,a} \\
         Z_{1,b} \\
         Z_{2,a} \\
         Z_{2,b} \\
         m_{a} \\
         m_{b}
    \end{array}
    \right),
\end{equation}
and this part of the equation then becomes:
\begin{eqnarray}\label{part1:phi4}
&& P \left( Z_{1,a} \leq \frac{t_a-m_{a}}{s_{a}}, 
Z_{1,b} \leq \frac{t_b-m_{b}}{s_{b}},Z_{2,b} \leq \frac{t_a-m_{a}}{s_{a}}, 
Z_{2,b} \leq \frac{t_b-m_{b}}{s_{b}} \right)  \\
&=&  \Phi_4 
\begin{pmatrix} 
\begin{bmatrix} t_a\\
t_b \\
t_a \\
t_b
\end{bmatrix};
E( \bV),Var(\bV)
\end{pmatrix} \nonumber.
\end{eqnarray}

The multivariate cumulative probabilities in two and four dimensions
are fast to compute using methods of \cite{genz2009computation}.  In
the end, the first part in Eq. (\ref{two_parts0}) and the second in
Eq. (\ref{part1:phi4}) are computed for each location on the grid, and
summing over the $x \in \mathcal{M}_g$, gives the design evaluation
criterion in Eq. (\ref{sur}). \kc{This might be a prevalent style in
  Math/Statistics, but this entire formulation is way too dense. I
  think it might be a good idea to have some basic intuition worked
  out early before the start of Sec 3}
